### 2022-03-03 paper1.tex
even more bib fixes
fix paper 1 tables, finish most of writing

\hypertarget{paper-1}{%
\chapter{Digital Trace Data as Indicators of Social Data Validating Google Trends for  use in Scientific Research}\label{paper-1}}

Possible titles Digital Trace Data as Social Indicators: Indicators of
Attention Rather Than Support

Digital Trace Data as Indicators of Social Data: Validating Google Trends for
 use in Scientific Research

\section{Abstract}

\section{Introduction}
New big data sources have led to vast possibilities for social science
research because they are bigger, cheaper, and already available
\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}. Before overenthusiastically embracing these
sources into our workflows, social scientists must clearly establish
parameters under which these data sources could be operationalized
\citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
prior research outlined, the "quantity of data does not mean that one
can ignore foundational issues of measurement and construct validity and
reliability and dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}. Building on this prior research outlining these various
issues with big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this paper tests the construct
validity of Google Search Trends as an indicator of three different
cases, namely cultural attitudes, disease prevalence and voting
behavior. These three cases will be tested using cultural indicators
from the NORC General Social Survey, United States county-level suicide
rates from National Center for Health Statistics, US cases rates of
Covid-19 from The New York Times, historical US Presidential Election
results, and the American National Election Survey. Data will be
analyzed against corresponding operationalized Google Trends
longitudinal data using Pearson's r for pairwise correlations, testing
for the strength of relationships between the Google Trend indicator and
the respective comparison indicator. This paper will contribute to the
creation of methodological norms and standards of how to use Google
Trends as a big data source for societal research and serve as a
critical inquiry into the adoption of big data without a critical eye
for the ecological validity of the sources.

With the expansion of big data, some research has shown extremely
innovative methods that lead to groundbreaking results that are shown to
be reliable. As an example, \citet{blumenstockPredictingPovertyWealth2015} use
county-level cell-phone records to construct the distribution of poverty
and wealth in Rwanda, a country where national surveys and censes are
rare and costly. However, \citet{blumenstockPredictingPovertyWealth2015} go to
great lengths to demonstrate that their operationalization of the cell
phone data creates a reliable and valid construct; few social science
papers utilizing big data dig into the construct validity of their
metrics to this extent and even fewer publications focus on
methodological guidelines of how to use sources of big data
\citep{asseoTrackingCOVID19Using2020, stilesAssessingCriterionValidity2018}.
However, research has shown the small adjustments to an algorithm or
metric may void any research insight we are able to pull from such data
\citep{lazerParableGoogleFlu2014}. Because of this, I propose a
methodological validation study of the Google Search Trends source of
big data to investigate how it is advisable to utilize this data in
social scientific research.

I will use three categorizations of ways I propose Google Trends could
be operationalized for social scientific usage. First, I'll test Google
Trends as an operationalization of cultural attitudes with the General
Social Survey. After \citet{bailCulturalEnvironmentMeasuring2014}'s call for
cultural sociologists to utilize the ever-expanding world of big data,
Google trends as a data source began appearing in sociological and
social science research. From research on mass shootings and firearms
\citep{brownsteinInternetSearchPatterns2020,semenzaInformationseekingWakeTragedy2020}, protest and anti-Muslim sentiment \citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017}, to analyzing country-level changes in social perception \citep{reyes_etal18},
Google search trends are a new and innovative indicator of cultural
interest. Extending into social networks and culture, \citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
how culture spreads around the globe.

Google Search Trends have also been used continuously in estimations of
disease prevalence and population health in journals like the Journal of
Medical Internet Research. While much of this research has focused on
the Covid-19 pandemic \citep{jimenez_etal20,jimenezCOVID19SymptomGoogle2020,limEstimatingInformationSeekingBehaviour2020,mavraganiCOVID19PredictabilityUnited2020,nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021} , other
research has investigated Google Trends as an indicator of wellbeing
\citep{brodeurCOVID19LockdownsWellbeing2021,carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
suicidality \citep{burnettTimeTrendsPublic2020}, vaccination uptake
\citep{dalumhansenEnsembleLearnedVaccination2016}, obesity
\citep{sarigulNowcastingObesityUsing2014}, and even insomnia
\citep{zittingGoogleTrendsReveal2020}, to cover a few examples. For a partial
review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
\citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
a correlation of \> .70, "demonstrating the vast potential of Google
Search as a proxy for monitoring population health" (p. 3) based on
assumptions that individuals search because of self-diagnosis and to
identify possible courses of treatment
\citep{dechoudhurySeekingSharingHealth2014}.

% <!-- Following reports say that Google searches can predict covid  -->

% <!-- 14. Brunori, P. & Resce, G. Searching for the peak Google Trends and the Covid-19 outbreak in Italy. SERIES working papers N. 04/2020 -->

% <!-- Lampos, V. et al. Tracking COVID-19 using online search. Preprint at https://arxiv.org/abs/2003.08086 (2020). -->

% <!-- 16. Walker, A., Hopkins, C. & Surda, P. The use of google trends to investigate the loss of smell related searches during COVID‐19 outbreak. Int. Forum Allergy Rh. 10, 839–847 (2020). -->

% <!-- 17. Stephens-Davidowitz, S. Google Searches Can Help Us Find Emerging Covid-19 Outbreaks. The New York Times https://www.nytimes.com/2020/04/05/opinion/coronavirus-google-searches.html (2020). -->

% <!-- 18. Frank, T. Goldman says fewer ‘loss of smell’ Google queries suggest better COVID outlook. Consumer News and Business Channel. CNBC https://www.cnbc.com/2020/04/15/goldman-says-fewer-loss-of-smell-google-searches-is-a-positive-sign-for-pandemic.html (2020) -->

Various sources have also used Google Trends as a way to forecast
political elections and political attitudes
\citep{wolfTrendingRightDirection2018}. For instance,
\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate
Elections relate to attention measured by search traffic.
\citet{prado-romanGoogleTrendsPredictor2020} compare how Google Search trends
are able to predict presidential election results in both the United
States and Canada. Finally, the OECD Development Centre is investigating
how Google data can help elucidate governments' approval in Latin
America \citep{montoyaUsingGoogleData2020}.

Research Question - How can we operationalize Google Search Trends as a
valid indicator for uses in social science research?

<https://journals.sagepub.com/doi/10.1177/0894439316631043> What
constructs might google trends capture and not capture well? Capture
attention but not attitudes

Also Asseo - "we assumed that media coverage may potentially decouple
the search popularity from the number of cases, since searches would
result not only from self-symptoms, but also from interest elicited by
media coverage."

@@

\subsubsection{Attitudinal}
<!-- \citep{gss_data} (let's see if I get access first) -->

One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
\citep{vaches_data}. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
of x observations, one for each U.S. County. The variable
measures the percent of adults in the county who describe themselves as
“unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
once one is available to them. The variable ranges from x to y.

Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
Dynata for the New York Times from July 2 through 14, 2020 \citep{mask_data}. 250,000
survey respondents were asked, "How often do you wear a mask in public when you
expect to be within six feet of another person?". The NYT weighted each response
to create a county level measure of what percent of the county never, rarely,
sometimes, frequently, and always wore a mask when in public. This dataset
consists of x observations, one for each U.S. County. This measure
represents the percent of adults in the county who never or rarely wear a mask
(range = x to x).

@@

I also use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from by \citet{covid_data}, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of 0 to a maximum of x for each 
Monday from x through x. There are x cases across x counties and x dates. Missing data were interpolated using `zoo::na.approx()` \citep{zoo}.

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year and can be interpreted as the
death rate by suicide for every 1000 people. There are x total
cases, resulting from x observations of x counties. Missing data were interpolated using
zoo::na.approx() \citep{zoo}. Measures range from x to x.

@@

Finally, I test Google Trends as an operationalization of political
attitudes by first looking at actual voting outcomes in historical US
Presidential Election results. This data comes from  \citet{pres_data}, who scraped the
results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
presidential outcomes were available for x counties in 2016 and
x counties in 2020. Each variable measures the percent of votes
for the candidate, with the lowest percent at x and the highest at x.

@@

\section{Discussion}

The external validity of these voting

While I expect these tests to show high correlation between observed
indicators and Google search trends, there will be three important
questions that surface. First, just because something is correlated,
does that mean it can replace the collection of other types of data?
Second, how correlated does a trend need to be for social scientists to
justifiably rely on it to indicate some outcome? And finally, how can we
construct analyses like this to be robust to changes in the terms used
across time and location?

The purpose of this paper is more methodological than theoretical, and I
see this paper having an impact on the social sciences and computational
social science as researchers pursue more projects using this source of
big data. Google Trends are relatively underutilized in the field
compared to in the health sciences and business. Once I assess how this
data can be used, I would like to be able to join
\citet{bailCulturalEnvironmentMeasuring2014} in encouraging social scientists
to pursue more research with big data while taking into account the
potential pitfalls with any source of big data
\citep{mcfarlandBigDataDanger2015}.

\section{Conclusion}

>>>>

\hypertarget{paper-1}{%
\chapter{Digital Trace Data as Indicators of the Social World: Validating Google Trends for use in Scientific Research}\label{paper-1}}

\section{Abstract}
I will first investigate how Google Search Trends can be operationalized
as cultural attitudes, disease prevalence and voting behaviors through
comparing trends data to observed valid indicators of these cases.
Specifically, I will test cultural indicators from the NORC General
Social Survey, United States county-level suicide rates from National
Center for Health Statistics, US case rates of Covid-19 from The New
York Times, historical US Presidential Election results, and the
American National Election Survey against selected Google Trends terms
and analyze the data using correlation methods. The aim of this article
is to assess the construct validity and will contribute to critical big
data studies and sociological methodology.

\section{Introduction}
New big data sources have led to vast possibilities for social science
research because they are bigger, cheaper, and already available
\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
Before overenthusiastically embracing these
sources into our workflows, social scientists must clearly establish
parameters under which these data sources should be operationalized
\citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
prior research outlined, the "quantity of data does not mean that one
can ignore foundational issues of measurement and construct validity and
reliability and dependencies among data" 
\citep[p. 1203]{lazerParableGoogleFlu2014}.

With the expansion of big data, some computational social science research has developed extremely
innovative methods that lead to groundbreaking results using big data that are shown to
be reliable. As an example, \citet{blumenstockPredictingPovertyWealth2015} use
county-level cell-phone records to construct the distribution of poverty
and wealth in Rwanda, a country where national surveys and censuses are
rare and costly. However, \citet{blumenstockPredictingPovertyWealth2015} go to
great lengths to demonstrate that their operationalization of the cell
phone data creates a reliable and valid construct; few social science
papers utilizing big data dig into the construct validity of their
metrics to this extent and even fewer publications focus on
methodological guidelines of how to use sources of big data
\citep[For exceptions, see ][]{asseoTrackingCOVID19Using2020, stilesAssessingCriterionValidity2018}.
However, research has shown the small adjustments to an algorithm or
metric may void any research insight we are able to pull from such data
\citep{lazerParableGoogleFlu2014}.

\subsection{Google Trends}

One source of big data that has yet to be widely utilized are Google Search Trends. 
Google Trends is an open data resource provided by Google, a major internet search
engine worldwide, that analyzes the top search queries across different localities, languages, and time. 
While Google Trends is freely available and holds a breadth of online activities that could potentially 
be of use in social science, few social scientists have used this resource. Because of this, 
I set out to establish how can we operationalize Google Search Trends as
validated indicator for uses in social science research to provide guidance to social scientists as they
adapt different sources of big data into their toolboxes.

Building on this prior research outlining various issues with different sources of big data
\citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015},
this paper tests the construct validity of Google Search Trends as an indicator of three different
cases, namely attitudes, disease prevalence and political preferences.
These three cases will be tested using attitudinal indicators from the %NORC General Social Survey, 
CDC \citeyearpar{vaches_data} and New York Times \citeyearpar{mask_data}, 
health indicators from the CDC \citeyearpar{suic_data}, 
US cases rates of Covid-19 from The New York Times \citeyearpar{covid_data},  
and political indicators from the historical US Presidential Election results \citeyearpar{pres_data}, 
and the American National Election Survey \citeyearpar{anes_data}. This paper will contribute to the
creation of methodological norms and standards of how to use Google
Trends as a big data source for societal research and serve as a
critical inquiry into the adoption of big data without a critical eye
for the ecological validity of the sources.

\subsection{Google Trends and research on attitudes}

I will use three categorizations of ways I propose Google Trends could
be operationalized for social scientific usage. First, I'll test Google
Trends as an operationalization of attitudinal indicators. 
After \citet{bailCulturalEnvironmentMeasuring2014}'s call for
cultural sociologists to utilize the ever-expanding world of big data,
Google trends began appearing as a data source in sociological and
social science research. From research on mass shootings and firearms \citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020}, 
protest and anti-Muslim sentiment \citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
to analyzing country-level changes in social perception \citep{reyes_etal18},
Google search trends are a new and innovative indicator of cultural interest.
Extending into social networks and culture, \citet{bailPrestigeProximityPrejudice2019}
even used Google trends to measure how 'culture' spreads around the globe.

\subsection{Google Trends and research on health behaviors}

Google Search Trends have been used continuously in estimations of
disease prevalence and population health in journals like the Journal of
Medical Internet Research. While much of this research has focused on
the Covid-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021},
other research has investigated Google Trends as indicators of wellbeing
\citep{brodeurCOVID19LockdownsWellbeing2021, carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
suicidality \citep{burnettTimeTrendsPublic2020}, 
vaccination uptake \citep{dalumhansenEnsembleLearnedVaccination2016}, 
obesity \citep{sarigulNowcastingObesityUsing2014}, 
and even insomnia \citep{zittingGoogleTrendsReveal2020},
to cover a few examples. For a partial review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
\citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
a correlation of \> .70, "demonstrating the vast potential of Google
Search as a proxy for monitoring population health" (p. 3) based on
assumptions that individuals search because of self-diagnosis and to
identify possible courses of treatment \citep{dechoudhurySeekingSharingHealth2014}.

\citet{mingUnderstandingHealthCommunication2021}

\subsection{Google Trends and research on politics}

Various sources have also used Google Trends as a way to forecast
political elections and political attitudes
\citep{wolfTrendingRightDirection2018}. For instance,
\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate
Elections relate to attention measured by search traffic.
\citet{prado-romanGoogleTrendsPredictor2020} compare how Google Search trends
are able to predict presidential election results in both the United
States and Canada. Finally, the OECD Development Centre is investigating
how Google data can help elucidate governments' approval in Latin
America \citep{montoyaUsingGoogleData2020}. 
% TODO what are the results of these papers? do they show promise?

\subsection{Causes for concern}
summarize
\citet{jungherr_etal17}

What constructs might google trends capture and not capture well? Capture
attention but not attitudes

In contrast to the papers mentioned above, there are researchers who have cautioned against
the wide usage of Google Search Trends. For instance, \citet{asseoTrackingCOVID19Using2020} 
concludes in their research on Covid-19 case rates and Google searches that the correlation 
is often spurious and due to confounding. They even explain that "searches would
result not only from self-symptoms, but also from interest elicited by
media coverage" \citep[][TODO ADD Page here]{asseoTrackingCOVID19Using2020}.

\citet{rovetta21}

\citet{cebrian_domenech22}

@@

\subsubsection{Attitudinal}

% <!-- \citep{gss_data} (let's see if I get access first) -->

One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
\citep{vaches_data}. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
of 3,148 observations, one for each U.S. County. The variable
measures the percent of adults in the county who describe themselves as
“unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
once one is available to them. The variable ranges from 4.99\% to 32.33\%.

Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
Dynata for the New York Times from July 2 through 14, 2020 \citep{mask_data}. 250,000
survey respondents were asked, "How often do you wear a mask in public when you
expect to be within six feet of another person?". The NYT weighted each response
to create a county level measure of what percent of the county never, rarely,
sometimes, frequently, and always wore a mask when in public. This dataset
consists of 3,148 observations, one for each U.S. County included in the sample. This measure
represents the percent of adults in the county who never or rarely wear a mask
(range = 0.10\% to 55.80\%).

@@

I also use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from by \citet{covid_data}, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of 0 to a maximum of 1460.46 for each Monday from January 27, 2020 through
December 27, 2021. There are 285,986 cases across 3,136 counties and 101
dates. Missing data were interpolated using `zoo::na.approx()` \citep{zoo}.

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year and can be interpreted as the
death rate by suicide for every 1000 people. There are 34,683 total
cases, resulting from 34,617 observations of 3,147 counties. Missing data were interpolated using
zoo\:\:na\.approx() \citep{zoo}. Measures range from 0.034 to 53.254.

@@

Finally, I test Google Trends as an operationalization of political
attitudes by first looking at actual voting outcomes in historical US
Presidential Election results. This data comes from  \citet{pres_data}, who scraped the
results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
presidential outcomes were available for 3,147 counties in 2016 and
3,118 counties in 2020. Each variable measures the percent of votes
for the candidate, with the lowest percent at 3.09\% and the highest at 92.15\%.

@@

\section{Discussion and Conclusion}
This paper provides a critical test of Google Trends for use in Social Science. 
I failed to find moderate or strong correlation among any of the Google 
Trends tested and their validated indicators.
While some Google Trends tested were significantly associated with the outcome in the linear regression model,
effects tended to be small and the total model explainability remained low,
even when controlling for demographic variables.

Some previous research has shown strong innovation in the computational social sciences
to gather sociodemographic data when survey or other research methods are too costly
\citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in theory, sounds like 
a promising data source to 'nowcast' attitidinal, health, and political indicators;
not only would the data be easily and freely accessible, it would also provide 
indicators for areas where conducting research may be too costly. The demand for this 
sort of indicator is clear and fields like the health sciences have freely utilized
this data source. However, this article shows that there is no 
no external validity of Google Trends for this specific use and social scientists
will find no replacement for high quality survey data with Google Trends.

As social scientists it is our responsibility to deeply investigate the validity 
of the data that we use in order to be confident in our research findings. As with any
source of data, we must take into account the potential pitfalls, especially in research on big data
\citep{mcfarlandBigDataDanger2015}. In the case of Google Search Trends, precaution was 
warranted. While I would like to be able to join \citet{bailCulturalEnvironmentMeasuring2014} 
in encouraging social scientists to pursue more research with the many new sources of big data, 
I emphasize that testing out data to verify what it actually corrresponds to is an essential step 
to making impactful research as a discipline going forward.

### 2022-03-03 paper3.tex
fix paper 1 tables, finish most of writing

While much of the social contagion literature, like the theories above, focuses
on structural boundaries and homophily as causes of how diffusion occurs,
\citet{goldbergSocialContagionAssociative2018} propose a
disrupting alternative mechanism. They argue that what actually diffuses during
social contagion are the perceptions about which beliefs or behaviors are
compatible with one another, what they call ``associative diffusion.'' This
argument that culture does not spread like a virus but instead is dependent on
how belief structures are connected to each other is important to test because
norms around health behaviors became politicized issues during the Covid-19
pandemic. This means that the stay-at-home or vaccination behavior themselves
were not contagious, but the cognitive association of precisely what social
distancing or vaccination uptake \emph{meant} were spreading between populations of
individuals. Moreover, as \citet{houghtonSocialContagionInteracting2021} outlines, diffusants - the things that are
diffusing through a population, are not independent of each other \citep{mason_etal07}. When we take into account the interdependence between different beliefs that are diffusing, such as Covid-19 is a hoax, social distancing saves
lives, the Covid-19 vaccine includes a microchip to control your thoughts, and lockdown
is against the rights guaranteed in the US constitution, we can imagine how
these various diffusants become associated together into structures of belief
through schemas of perception \citep{houghtonSocialContagionInteracting2021}. While this cognitive theory of cultural variation is difficult to test, the theory it supplies provides a solid framework for how behavioral norms formed during the pandemic.

@@

To operationalize the search for online norms, I use Google search trends \citep{googletrends},
over the study period across individual designated media markets areas (DMAs), a
nonoverlapping aggregation of U.S. counties to 210 media markets based on
similar population clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
online in both cases, I use the following search topics: `Social Distancing'
(2020, stay-at-home case only), `Covid-19 Vaccine' (2021, vaccination uptake case
only) and Covid Conspiracy (2020-2021, both cases). Search topics are a more
robust measurement than a single search term: topics are aggregations of the
rates of multiple, highly correlated search terms together into a cohesive
topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
separate search terms, `Beyoncé Knowles' encompasses all of these into a single
search topic. While the data is originally on a scale of 0 to 100, with
100 being the maximum search popularity out of all DMAs, Google Search Trend are
now only available cross-sectionally (a single time period across a geography)
or time-series (a single geo-location across time). To remedy this and build a
longitudinal dataset of each search topic, I follow the method proposed in
Park, Kwak, and An (n.d.) (p.~5). This method involves building a dataset of unscaled
cross-sectional values, selecting a DMA to use to establish the rescaling ratio
(I use `Los Angeles CA'), and then finding the time-series values for the one
DMA. To find the rescaling ratio for each week in the time-series, you divide
the time-series value for each week by the cross-sectional value for each week,
resulting in a rescaling vector to be used for all weeks in the dataset across
geographies. To rescale each longitudinal value, multiply the respective week's
rescaling ratio by the cross-sectional value. Rescaled longitudinal data was
compared against time-series data for multiple test counties and was equivalent.
For a more in-depth explanation of this procedure, see \citet[p. 5]{park_etal}.

>>>>

While much of the social contagion literature, like the theories above, focuses
on structural boundaries and homophily as causes of how diffusion occurs,
\citet{goldbergSocialContagionAssociative2018} propose a
disrupting alternative mechanism. They argue that what actually diffuses during
social contagion are the perceptions about which beliefs or behaviors are
compatible with one another, what they call ``associative diffusion.'' This
argument that culture does not spread like a virus but instead is dependent on
how belief structures are connected to each other is important to test because
norms around health behaviors became politicized issues during the Covid-19
pandemic. This means that the stay-at-home or vaccination behavior themselves
were not contagious, but the cognitive association of precisely what social
distancing or vaccination uptake \emph{meant} were spreading between populations of
individuals. Moreover, as \citet{houghton20} outlines, diffusants - the things that are
diffusing through a population, are not independent of each other \citep{mason_etal07}. When we take into account the interdependence between different beliefs that are diffusing, such as Covid-19 is a hoax, social distancing saves
lives, the Covid-19 vaccine includes a microchip to control your thoughts, and lockdown
is against the rights guaranteed in the US constitution, we can imagine how
these various diffusants become associated together into structures of belief
through schemas of perception \citep{houghton20}. While this cognitive theory of cultural variation is difficult to test, the theory it supplies provides a solid framework for how behavioral norms formed during the pandemic.

@@

To operationalize the search for online norms, I use Google search trends \citep{googletrends},
over the study period across individual designated media markets areas (DMAs), a
nonoverlapping aggregation of U.S. counties to 210 media markets based on
similar population clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
online in both cases, I use the following search topics: `Social Distancing'
(2020, stay-at-home case only), `Covid-19 Vaccine' (2021, vaccination uptake case
only) and Covid Conspiracy (2020-2021, both cases). Search topics are a more
robust measurement than a single search term: topics are aggregations of the
rates of multiple, highly correlated search terms together into a cohesive
topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
separate search terms, `Beyoncé Knowles' encompasses all of these into a single
search topic. While the data is originally on a scale of 0 to 100, with
100 being the maximum search popularity out of all DMAs, Google Search Trend are
now only available cross-sectionally (a single time period across a geography)
or time-series (a single geo-location across time). To remedy this and build a
longitudinal dataset of each search topic, I follow the method proposed in \citet[p. 5]{park_etal}.
This method involves building a dataset of unscaled
cross-sectional values, selecting a DMA to use to establish the rescaling ratio
(I use `Los Angeles CA'), and then finding the time-series values for the one
DMA. To find the rescaling ratio for each week in the time-series, you divide
the time-series value for each week by the cross-sectional value for each week,
resulting in a rescaling vector to be used for all weeks in the dataset across
geographies. To rescale each longitudinal value, multiply the respective week's
rescaling ratio by the cross-sectional value. Rescaled longitudinal data was
compared against time-series data for multiple test counties and was equivalent.
For a more in-depth explanation of this procedure, see \citet[p. 5]{park_etal}.

### 2022-03-03 tables/paper1/data-sources-table.tex
fix paper 1 tables, finish most of writing

\begin{table}[!h]
\caption{\label{tab:data-sources-table}}
\centering
\begin{tabular}[t]{}
\end{tabular}
\end{table}

>>>>

\newcolumntype{L}{>{\raggedright\arraybackslash}X}

\definecolor{Gray}{gray}{0.9}
\definecolor{lightblue}{HTML}{bad7db}

\renewcommand{\arraystretch}{1.2}

\begin{table}[!h]
\caption{\label{tab:data-sources-table}Data Sources}
\centering
\fontsize{8}{10}\selectfont
\setlength{\extrarowheight}{2pt}
\begin{tabularx}{\linewidth}{@{}L c c L@{}}
\toprule
\textbf{Validated Data Source} & \textbf{Type} & \textbf{Dates} & \textbf{Google Trends Used}\citep{googletrends} \\ \midrule
% \rowcolor{lightblue}
\multicolumn{4}{l}{\textbf{Behaviors and Attitudes}} \\\hline
% General Social Survey & Cross-Sectional & 2010 - 2020 & NA \\
Vaccine Hesitancy for COVID-19 \citep{vaches_data}& Cross-Sectional & March 3 - 15, 2021 & Search Topics: 'Covid-19 vaccine', 'Coronavirus (Disease)', 'Coronavirus   (Virus)', 'Vaccine' \\
Mask-Wearing Survey Data \citep{mask_data} & Cross-Sectional & July 2 - 14, 2020 & Search Topics: 'Coronavirus (Disease)', 'Coronavirus (Virus)', 'Cloth   Face Mask', 'Mask', 'Civil and Political Rights' \\
American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
% \rowcolor{lightblue}
\multicolumn{4}{l}{\textbf{Health}} \\\hline
Covid Rates \citep{covid_data}& Longitudinal & Every Monday, 2020 - 2021 & 'Covid-19', 'Coronavirus', 'Taste Loss', 'Smell Loss' \\
Suicide Rates \citep{suic_data} & Longitudinal & Yearly 2010-2020 & Search Topics: 'Suicide', 'Depression', Search Term:' Suicide Hotline' \\
% \rowcolor{lightblue}
\multicolumn{4}{l}{\textbf{Political}} \\\hline
American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
Presidential Election Results \citep{pres_data}& Cross Sectional & 2016 \& 2020 & Search Topics: 'Hilary Clinton', 'Donald Trump', 'Joe Biden' \\ \bottomrule
\end{tabularx}
\end{table}

### 2022-03-03 tables/paper2/model-2-phi.tex
fix paper 1 tables, finish most of writing

\begin{table}[!h]

\caption{\label{tab:model-2-phi}Phi Coefficient ($\phi$) of binary association between each Information Search Vehicle}
\centering
\begin{tabular}[t]{p{0.25\linewidth} p{0.10\linewidth} p{0.08\linewidth} p{0.12\linewidth} p{0.15\linewidth} p{0.12\linewidth}}
\hline
 & Person & Dr & Online Forum & Social Networking Site & Online Search\\
\hline
\cellcolor{gray!6}{Person} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.28} & \cellcolor{gray!6}{0.172} & \cellcolor{gray!6}{0.275} & \cellcolor{gray!6}{0.216}\\

Dr & NA & NA & 0.192 & 0.152 & 0.098\\

\cellcolor{gray!6}{Online Forum} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.371} & \cellcolor{gray!6}{-0.073}\\

Social Networking Site & NA & NA & NA & NA & 0.057\\

\cellcolor{gray!6}{Online Search} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA}\\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]

\caption{\label{tab:model-2-phi}Phi Coefficient ($\phi$) of binary association between each Information Search Vehicle}
\centering
\begin{tabular}{p{0.25\linewidth} p{0.10\linewidth} p{0.08\linewidth} p{0.12\linewidth} p{0.15\linewidth} p{0.12\linewidth}}
\hline
 & Person & Dr & Online Forum & Social Networking Site & Online Search\\
\hline
Person& NA& 0.28& 0.172& 0.275& 0.216\\

Dr & & & 0.192 & 0.152 & 0.098\\

Online Forum& NA& NA& NA& 0.371& -0.073\\

Social Networking Site & & & & & 0.057\\

Online Search& NA& NA& NA& NA& NA\\
\hline
\end{tabular}
\end{table}
